\chapter{Survey Items Used in Chapters \ref{chap:evilndi}, \ref{chap:prondi},
    \& \ref{chap:mechanism}}
\label{app:survey-items}

\extrarowsep 5pt
\begin{longtabu}{>{\sffamily}rX}
\caption{Demographic questions. Numeric codes assigned by survey software are given in
    parentheses and not shown to participants. If no list of choices is given
    for a question, a blank space was provided. \label{table:demographics}} \\
\toprule
\textrm{Question ID} & Wording / Answers \\
\midrule
\endfirsthead

\caption[]{Demographic questions, continued} \\
\toprule
\textrm{Question ID} & Wording / Answers \\
\midrule
\endhead

\bottomrule
\endfoot

state & In what U.S. state or territory to you reside? Please use the 2-letter
abbreviation (e.g., MD, DC, PR) \\

gender & What is your gender? \\
 & Male (1), Female (2) \\

citizen & Are you a U.S. citizen or permanent resident? \\
 & Yes (1), No (2) \\

us_born & Were you born in the U.S.? \\
 & Yes (1), No (2) \\

english & Is English your first language? \\
 & Yes (1), No (2) \\

party & What is your strongest political party affiliation? \\
 & None (1), Democrat (2), Green (3), Independent (4), Libertarian (5),
 Republican (6), Other (7), Decline to State (8) \\

conserv & On the following scale, indicate the extent to which you consider
yourself to be liberal or conservative on most political and social issues: \\
 & 1 Extremely Liberal, 2, 3 Somewhat Liberal, 4, 5 Moderate, 6, 7 Somewhat
 Conservative, 8, 9 Extremely Conservative (numerical scale given to
 participants) \\

faith & What is your main religious faith? \\
 & Atheist (1), Agnostic (2), Buddhist (3), Christian (4), Hindu (5), Jewish (6),
Muslim (7), Spiritual but not religious (8), Other (9), Decline to state (10) \\

ed_level & What is the highest level of education you have completed? \\
 & No higher than 8th grade (1), Some high school (9-12th grade) (2), High
 school diploma / GED (3), Some college (4), Bachelor's degree (5), Master's
 degree (6), Professional degree (7), Doctoral degree (8) \\

cc_inst & Have you received any instruction regarding Global Warming (Climate
Change) in the last 2 years? If so, when was the most recent? \\
 & No (1), Fall 2012 (2), Summer 2012 (3), Spring 2012 (4), Winter 2011-2012
 (5), Fall  2011 (6), Summer 2011 (7), Spring  2011 (8), Winter 2010-2011 (9) \\

cci_desc & Please describe the instruction you've received regarding Global
Warming (Climate Change) \\

us_years & You indicated that you were born outside the U.S. How many years have
you been living in the U.S.? (Please round up to the nearest whole number.) \\

where_born & Where were you born? \\

eng_years & How many years have you been speaking English? \\

first_lang & What is your first language? \\
\end{longtabu}

\begin{longtabu}{>{\sffamily}rX}
\caption{Belief / attitude (“RTMD”) questions used in the various studies. Most
    items were on a 1–9 scale (noted below the table). Scales for items that
    deviate are reported below the question.  \label{table:rtmd-questions}} \\
\toprule
\textrm{Question ID} & Wording / Answers \\
\midrule
\endfirsthead

\caption[]{Belief / attitude (“RTMD”) questions.} \\
\toprule
\textrm{Question ID} & Wording / Answers \\
\midrule
\endhead

\bottomrule
\multicolumn2{p{\linewidth}}{1–9 scale usually consisted of: 
Extremely Disagree 1, Strongly Disagree 2, Disagree 3, Mildly Disagree 4,
Neither Agree Nor Disagree 5, Mildly Agree 6, Agree 7, Strongly Agree 8,
Extremely Agree 9. Where different, the scale is noted in the table next to the
question above.} \\
\endfoot

evo1_1 & Evolution accurately explains how plants, animals, and humans came
to be as they are. \\

gw1_2 & Human activities are largely responsible for the climate change
(global warming) that is going on now. \\

nat1_3 & The United States is one of the very best countries on our planet
(e.g., “in the top three”). \\

dty1_4 & There exists a supernatural being/deity (e.g., God) or set of beings/deities (gods). \\

aft1_5 & After a person dies, that person experiences an afterlife of some sort (for instance, heaven/hell, reincarnation, enlightenment, nirvana, etc.). \\

cre1_6 & Biblical creation accurately explains how plants, animals, and humans came to be as they are. \\

gw2_1 & Global warming or climate changes, when they happen at all, are just parts of a natural cycle. \\

gw2_2 & I am certain that global warming is actually occurring. \\

gw2_3 & I am worried about global warming. \\

gw2_4 & Humans are severely abusing the environment. \\

evo2_5 & Evolution is unable to explain much of the physical evidence regarding the origins and development of life on Earth. \\

evo2_6 & Other living things may have evolved, but humans have not. \\

lifsty & Overall, how important is it to change your current lifestyle to reduce your carbon footprint (i.e., to decrease the amount of greenhouse gases you emit both directly and indirectly)? \\
 & Not Important 1, 2, Slightly Important 3, 4, Somewhat Important 5, 6, Very Important 7, 8, Extremely Important 9 \\

engage & I intend to personally engage in more environmentally-friendly (e.g., sustainable, recycling, and/or resource-minimizing) activities in the future, compared to what I do now. \\

aft2 & After a person dies, that person lives on in some way. \\

aft3 & I don't believe that heaven exists. \\

dty2 & God is created by human imagination. \\

dty3 & The only true God is that of my religion. \\

cre2 & A supreme being has never played any role in the origin or development of life on earth. \\

cre3 & To me, creation gives a more satisfying explanation of life on Earth than does evolution. \\

nat2 & The United States can fix just about any problem it might unintentionally create. \\

natmil & How many countries could defeat the U.S. militarily without assistance from other countries? \\
 & \underline{\hspace{3cm}} Countries \\

knwgbl & Please indicate how knowledgeable you think you are about climate
change—by choosing a number on the 1 (not knowledgeable at all) to 9 (extremely
knowledgeable) scale below. \\
 & Not knowledgeable at all about Climate Change 1, 2, 3, 4, Moderately
 knowledgeable about Climate Change 5, 6, 7, 8, Extremely knowledgeable about
 Climate Change 9 \\
\end{longtabu}
