\documentclass[12pt]{myucthesis}

% \nofiles
% The above command prevents latex from writing its auxiliary
% files. This is useful if you want to manually tweak them before you
% generate your final PDF. But it will break reference / bibliography
% resolution!

% This lets us load OpenType fonts from the system without any fuss. 
% It's already required by unicode-math, but I include it for reference.
\usepackage{fontspec}

% \usepackage{amsmath,amssymb}

% Note that if you use unicode-math, you need to do it after amsmath (and
% prehaps other ams things, and certainly mathtools)

% These are options that don't matter to this document!
% \usepackage[partial=upright,nabla=upright]{unicode-math}

% Note that none of the 4 styles available in unicode-math adhere to APA! french
% is closest / easiest, as only upper-case latin characters are wrong (they should
% be italicised, but they are not). Can use \mathit
\usepackage[math-style=french]{unicode-math}
% What can I say, I love the french
\frenchspacing

% microtype enables subtle typography improvements.
% Note that in XeTeX, expansion is disabled, and so some line breaks get screwed
% up (and you need to manually include hyphens or similar)
\usepackage{microtype}
\DisableLigatures{family = tt*}

% This keeps things like `` and --- working
\defaultfontfeatures{Ligatures=TeX}

% All below are freely available fonts, and are likely included with your TeX
% distro

% NB: Numbers=OldStyle can only be used on the regular Pagella font
% The Microtype option for set*font is redundant with the microtype package
\setmainfont{TeX Gyre Pagella} % One of few fonts with OpenType math
\setsansfont{TeX Gyre Heros} % Seems OK
% \setsansfont{DejaVu Sans}
\setmonofont{Inconsolata} % Skinny and easy on the eyes
% \setmonofont{TeX Gyre Cursor} % This font sucks
\setmathfont{TG Pagella Math}

% Page layout. The fancyhdr package may complain about the need for a
% larger headheight, depending on how long chapter titles are; if left
% unspecified in the geometry setup, it defaults to 12pt. The
% "showframe" option causes the geometry package (version >= 5.0) to
% show a frame around the margins on every page, which is great for
% checking that you don't overflow anywhere.

% geometry driver auto detection may not work for XeLaTeX below
% \usepackage[letterpaper,includehead,margin=1in,headheight=15pt,showframe]{geometry}
\usepackage[letterpaper,includehead,margin=1in,headheight=15pt]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\lhead[\fancyplain{\thepage}{\thepage}]{\fancyplain{}{\scshape\rightmark}}
\rhead[\fancyplain{}{\scshape\leftmark}]{\fancyplain{\thepage}{\thepage}}
\chead{}
\cfoot{}
\lfoot{}
\rfoot{}


% Bibliography stuff:
% DJC - I'm now using biblatex and bilatex-apa
% This is 1i18n overkill, including i18n of quotes
% Also - folks seem to think polyglossia is better now (but it only works in
% XeTeX, not LuaTeX in TeX Live 2012)
\usepackage[american]{babel}
\usepackage{csquotes}

% uniquelist fixes a bug in mis-interpreting APA section 6.12, fixed in v. 6.1
% of the apa style
\usepackage[style=apa,uniquelist=minyear,backend=biber]{biblatex}

% More i18n overkill
\DeclareLanguageMapping{american}{american-apa}

\addbibresource{thesis.bib}
\addbibresource{fixed.bib}

% Other setup:

\usepackage{graphicx}

% DJC - my extra packages here
\usepackage[labelfont=it]{caption}
% This is where warnings about the caption package used to come from
\usepackage{subfig,multirow,hologo,underscore}
% Make it easier to print complicated tables
\usepackage{longtable,siunitx,tabu}
% This might be useful for simpler tables. For text heavy tables with
% Excel-style CSV, tex-based solutions are going to choke!
% \usepackage{pgfplotstable}
% Mostly just to supress a warning
% \pgfplotsset{compat=1.8}
% \pgfplotstableset{sci zerofill}%,col sep=comma}

% pgfplotstable recommends
% This will allow some of the nicer layout options for number alignment, etc.
% \usepackage{array}

% Better spacing and rules (lines, not laws)
\usepackage{booktabs}

\usepackage{enumitem}
\setlist{itemsep=0pt}

\usepackage{pdfpages}
\usepackage{minted}

% Note: with BibLaTeX, you should load hyperref after the biblatex package. And
% according to the WikiBook - it should be loaded close to last.
\usepackage[pdfborder={0 0 0},pdfusetitle]{hyperref}
% This was the original hyperref inclusion with color
% \usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue,pdfusetitle]{hyperref}

\begin{document}
\ssp % single spacing
\hypersetup{pageanchor=false}
\include{setup}
\maketitle
\copyrightpage

\begin{abstract}

Global Warming\footnote{I (and many others) prefer the term “Climate Change.”
    Even though changes in atmospheric chemistry will force the mean temperature
    of the globe higher, the effects will complicated by climate systems,
    resulting in---at least in the short term---local cooling in some places and
    a variety of other changes in weather patterns. However, as we'll be
    focusing primarily on the physical mechanisms by which the earth is warming,
    we'll use the more colloquial term “Global Warming” in this dissertation.}
(“GW”) is easily one of the most pressing concerns of our time, and its solution
will come about only through a change in human behavior.  Compared to the
residents of most other nations worldwide, Americans report lower acceptance of
the realities of GW.  In order to address this concern in a free society, U.S.
residents must be convinced or coerced to take the necessary actions. In spite
of the democratic appeal of education, however, many climate communicators appear to
be settling on the notion that emotional persuasion is superior to education.

We'll set an empirical foundation in Chapter~\ref{chap:two}, reviewing an
experiment in the Numerically Driven Inferencing (NDI) paradigm that sheds some
light on the cognitive processes involved in learning and attitude shifts in
response to surprising policy-relevant information.
Chapters~\ref{chap:survey}--\ref{chap:mechanism} contain results from a
comprehensive program of research specifically targeting climate-related
attitudes and beliefs in the United States. As alluded to above, there have been
many surveys of American attitudes. Chapter~\ref{chap:survey} provides an
overview of our approach to assessing climate-related beliefs and attitudes. In
particular, we note relationships observed in one survey between scientific
literacy regarding the GW mechanism on one hand and attitudes, including
“willingness to sacrifice” on the other. As with some other empirical
approaches, our results suggest that U.S.  residents generally accept
anthropogenic (i.e., “human caused”) climate change, and support action on this
issue. But even if this is the case, Chapter~\ref{chap:evilndi} describes an
experiment demonstrating that these beliefs and attitudes are disturbingly
fragile in the face of cherry-picked, misleading numerical facts.
Chapter~\ref{chap:prondi} then describes a pair of experiments evaluating the
effects of representative numerical facts. Chapter~\ref{chap:prondi}'s Study~1
(Section~\ref{sec:pro-uc}) demonstrates that even when students report strong
psychological effects after receiving a set of surprising numbers, their beliefs
and attitudes will not necessarily be affected. Chapter~\ref{chap:prondi}'s
Study~2 (Section~\ref{sec:pro-mturk}) improves upon the clarity of materials
used in Study~1 and demonstrates that such materials \emph{can} effectively
increase climate change acceptance and concern. In both of these studies, as
with the study presented in Chapter~\ref{chap:evilndi}, this relatively
uncontextualized, surprising numerical information undermines students'
confidence in their own knowledge. Chapter~\ref{chap:mechanism} reports on three
successful experiments (spanning four samples) that provide a coherent
explanation of the mechanism of climate change that includes relevant numerical
facts. As with Study~2 in Chapter~\ref{chap:prondi}, this intervention shifts
participant attitudes towards the scientific consensus.  Unlike uncontextualized
numerical information, however, this mechanism intervention additionally leaves
participants feeling that they know more than they did prior to instruction.
Chapter~\ref{chap:mechanism}'s Study~1 (Section~\ref{sec:mech-classroom})
establishes this effect in classroom-based settings at two culturally distinct
universities.  Chapter~\ref{chap:mechanism}'s Study~2
(Section~\ref{sec:mech-uc-online}) provides an initial evaluation of the
time-course of retention for the cognitive shifts that followed our mechanism
intervention, and Chapter~\ref{chap:mechanism}'s Study~3
(Section~\ref{sec:mech-mturk}) provides a successful demonstration of durable
shifts with the general population online.

Taken together, these experiments point the way towards effective curricula and
on-line materials that can help bolster support to combat climate change. While
we must certainly be sensitive to the needs, values, and interests of our target
audiences, we should not reflexively steer away from science education. Indeed,
the experiments in this dissertation provide empirical support for the notion
that science education materials can have a meaningful and lasting impact on GW
attitudes and beliefs. While this may not provide the complete behavioral
solution we need for the United States (and the world), it seems likely that
such shifts will make behavioral and policy changes far more tractable in the
coming years.

\end{abstract}

% another hyperref config
\hypersetup{pageanchor=true}
\begin{frontmatter}

\begin{dedication}
\null\vfil
{\large
\begin{center}
With love and respect for all that is good---in particular the unwavering
support of my grandma (even if she doesn't fully accept climate change \emph{or}
evolution).
\end{center} }
\null\vfil
\end{dedication}

\tableofcontents
\listoffigures % optional
\listoftables % optional

% If using code.sty, can also add:
% \listofcodes
% \addcontentsline{toc}{chapter}{List of Code Examples}
% Or we could use listings
% \lstlistoflistings

\begin{acknowledgements}

The tone of the following dissertation is one of success and hope. This,
however, is largely due to my attempts to satisfy the (perhaps imagined)
constraints of getting my dissertation submitted. At this moment, I still find
myself struggling to grapple with the daunting challenges of two systems that
place little value on genuine long-term thinking: the global economic system,
and the university system. Dear reader, I know you have to eat, but please do
your best to pay attention to the long-term consequences of your actions. You
might also ask your elected officials to do the same. And golly, do educators
need our help. And that person in the chicken suit who just shut down the
highway while you're trying to get to work? They're grappling with similar
issues too. I don't think any of us have even one complete answer. So, dear
reader, I'm glad you're joining me in the effort to find one.

Looking back, I must say that the brightest star in this particular journey was
Tawny Tsang. Her continued cheer and critical evaluation of my sometimes muddled
direction were more than I could ask for. 

I have also had many teachers. I call particular attention to Larry Goldfarb,
director for my training in the method developed by Moshe Feldenkrais. I have
great appreciation for all of the teachers that assisted Larry as well. This
work continues to provide me with inspiration for helping myself and others
develop healthier habits. Thanks also to Connie Cronin for being my longish-term
student---this allowed me to learn a lot. Looking back over my formal education,
I continue to believe that I was almost unfortunately lucky in the guidance and
attention I received as an undergraduate at the University of Maryland, College
Park. Between Bonnie Dorr, Amy Weinberg, Phil Resnik, Eric Slud, David
Lightfoot, and the other members of the CLIP lab, I managed to recieve an
incredibly rich introduction to the formal study of human language.  It took me
a while to realize that this experience, sadly, wasn't normal! At MIT, I
benefited from the instruction of Ken Wexler and Anthony Wagner, and at NYU, I
learned from Lila Davachi and Yadin Dudai.  I feel it's incumbent to mention my
first conversation with Tom Wickens when I was trying to get out of taking his
intro to statistics for psychology graduate students. He was quite reasonable
about it, saying that one could always benefit from a different treatment of the
material, but I wouldn't have any of it---I was still a punk kid at age 29.
Fortunately, I had to take his class in the end, and it was great. Thanks to
Rich Ivry and Michael Ranney for serving as co-chairs on my dissertation, and to
Sonia Bishop for her helpful (and early!) comments.  Extra special thanks to
John Canny, who gives me some small hope that perhaps one can do simultaneously
useful \emph{and} interesting things within the university context.

I was of course helped enormously by my friends and colleagues along the way.
Lila Davachi gets a double mention here. Particular thanks to Tim Anderson,
Meghan Ballog, Derek Clark, Sailor Neal, Dustin Stansbury, Emily Cooper, Boris
Fain, Dan Walsh, David Grefrath, and the rest of the gang at Ft. Awesome. And
you certainly can't make it through grad school without your fellow research
group members.  Thanks to John Schlerf, Flavio Oliviera and Jing Xu for
shepherding me into the CognAc lab, and thanks to Becca Elenzil, Ryan Morehead,
and Alex Carstensen for seeing me through. Daniel Reinholz was not only a
stalwart of the Reasoning group, but also directly assisted with much of the
research that follows. And a general thanks to members of the CognAc and
Reasoning groups. Thanks also for the timely help of Eti Valdez-Kaminsky. And
special appreciation for Cynthia Rauschert, who I feel has been on a parallel
struggle with me for many years now. Hopefully, we're both coming out the other
end!

And of course I owe a great debt to my family. My brother (Derek) gets the
second double mention here, and you've met my grandma, Anne Eccleston, in the
dedication. Then of course, there is my mother, Joanne Schmidt, and my father,
Mark Clark. Much love also to my sister, Stephanie Clark, my grandpa, Joe
Eccleston, and all my aunts, uncles, and cousins. Then there's the extended
family I've gained through various marriages. Thanks in particular to Darcy
Clark for welcoming me into her home to get me through some of these final
struggles. Thanks also to John Schmidt and Linda Clark.

More recently, I am fortunate to have made the acquaintance of The team at
Oroeco, and other climate crusaders. People have been trying and failing to
shift human behavior towards greater sustainability for decades. It is at this
point that I must simply check my modesty at the door and say that \emph{this
    time} we're going to get it right.

Lastly, I am grateful beyond words for the arrival of Madoka Wada in my life. I
had no idea someone could be wonderful like that.

This dissertation was based on the
\href{https://github.com/pkgw/ucastrothesis}{\textsf{ucastrothesis}} template.
It was typeset with \hologo{LuaLaTeX} using fonts from the \TeX\ Gyre project
(Pagella for main text and Heros for sans serif) and Inconsolata for monospaced
text. The research reported here was supported in part by the Institute of
Education Sciences pre-doctoral training grant R305B090026 to the University of
California, Berkeley and the University of California, Berkeley Committee on
Research. The opinions expressed are those of the author and do not necessarily
represent views of the Institute of Education Sciences, the U.S.  Department of
Education, or the University of California.

% Something about Amazon, Mechanical Turk, and whatever other trademarks I use
% in the document.

\end{acknowledgements}
\end{frontmatter}

% This makes my tabu tables have more spacing in them by default
\tabulinesep 5pt

\include{intro/intro}
\include{two-routes-estimation/two-routes-estimation}
\include{survey-methods/survey-methods}
\include{evil-ndi/evil-ndi}
\include{pro-ndi/pro-ndi}
\include{mechanism/mechanism}

% These are here only for historical reasons
% \include{experimental-description/experimental-aims}
% \include{experimental-description/experimental-plan}

\include{conclusion/conclusion}

\printbibliography[title=References,heading=bibintoc]

\appendix

\include{appendices/survey-items/survey-items}
\include{appendices/undp/undp}
\include{appendices/Evil-NDI-intervention/Evil-NDI-intervention}
\include{appendices/Pro-NDI-intervention/Pro-NDI-intervention}
\include{appendices/numbers/numbers}
\include{appendices/mech-intervention/mech-intervention}
\include{appendices/400words/400words}
\include{appendices/detecting-plagiarism/detecting-plagiarism}
\include{appendices/coding/coding}
\include{appendices/kappa-extension/kappa-extension}
\include{appendices/imputation/imputation}

% \include{appendices/graphical-models/graphical-models}

\end{document}
