\chapter{Numerical Information used in Chapter \ref{chap:prondi}}

Note that we do not report the specific information used in \ref{chap:evilndi},
as we have little desire to contribute to the precision of the already
formidable propaganda campaign arrayed against climate change acceptance.

The below is not formatted well for \hologo{LaTeX}.


Global surface temperatures have been recorded since 1850. According to the 2007 report from the Intergovernmental Panel on Climate Change, how many of the years between 1995-2006 (a 12 year period) are one of the hottest 12 years recorded?
"\# of years"
11 years

What is the change in the atmospheric levels of methane (a greenhouse gas) since 1750?
"\% increase" or "\% decrease"
151\% increase

What is the change in percentage of the world's ocean ice cover since the 1960s?
"\% increase" or "\% decrease"
40\% decrease

According to observation data collected at Mauna Loa Observatory in Hawaii, what is the percent change in atmospheric CO2 levels from 1959 (when observation began) to 2009?
"\% increase" or "\% decrease"
22.6\% increase

A 2010 article examines the 908 active researchers with at least 20 climate publications on Google Scholar. What percentage of them have stated that it is “very likely” that human-caused emissions are responsible for “most” of the “unequivocal” warming of the Earth in the second half of the 20th century?
"\% of researchers"
97.5\%

In 1850 there were approximately 150 glaciers present in Glacier National Park. How many are present today?
"\# of glaciers"
25 glaciers

From 1850 to 2004, what is the percent change of volume of glaciers in the European Alps?
"\% increase" or "\% decrease"
50\% decrease

(Note - actually reported 6.4 feet on all but final CCO studies - will be final
2 once I run Michael's proposed changes)
According to a study published in Geophysical Research Letters, by how much has the average sea level changed from 1870 to 2004?
"feet increase" or "feet decrease"
0.640 feet

