\chapter{Format of final NDI intervention}
\label{chap:format-ndi}

Below is an example format for an NDI-style estimation intervention.
Interventions consisted of 2-8 such estimations, and did not always include all
elements (see individual sections for details). Note also that I have not
adjusted the formatting to avoid \LaTeX\ defaults, such as indentation. 
\hrule
Global surface temperatures have been recorded since 1850. According to the IPCC
Fourth Assessment Report, released in 2007, how many of the years between
1995-2006 (a 12 year period) are one of the hottest 12 years of recorded global
temperature? My estimate is a…

number of years (out of 12)

The number I estimate is (whole numbers only):

How low and how high would that number have to be to surprise you?
Lower than: 
Higher than:

Approximately how confident are you that the actual value falls in the range
between the low and high numbers above? (Note that a confidence below 50 would
imply you think it is more likely that the number is outside your range!)

\underline{\hspace{3cm}} Percent Confidence (selected with slider ranging from
50–100)

 
On the previous page you estimated the following value:  Global surface
temperatures have been recorded since 1850. According to the 2007 report from
the Intergovernmental Panel on Climate Change, how many of the years between
1995-2006 (a 12 year period) are one of the hottest 12 years recorded?

The true value is: 11 years  Please note how this compares to the estimate you
gave: [estimate is inserted here] (number of years)

Did you find this number surprising?

Not Surprising at All 1, 2, 3, 4, Somewhat Surprising 5, 6, 7, 8, Extremely
Surprising 9

Briefly, what specifically did you find surprising (if anything)?

Were you surprised or embarrassed at your own lack of knowledge?

Not Surprised or Embarrassed at All 1, 2, 3, 4, Somewhat Surprised or
Embarrassed 5, 6, 7, 8, Extremely Surprised or Embarrassed 9

How novel or familiar is this information to you?

I've seen nothing like this 1, 2, 3, 4, I've seen similar information 5, 6, 7,
8, I've seen this exact informaiton 9 

Please describe anything you'd forgotten prior to reading the value above, but
now you remember (if anything):

Please describe any other thoughts or memories triggered by the above, including
if you have any points of disagreement or objection (if anything):
